---
title: "FA6"
author: "Paul Joaquin M. Delos Santos"
date: "2024-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question (1)
I. Geometric Distribution. Provide an R code for the geometric distribution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.

1. Set the probability of success:  p <- 0.2
2. Generate 1000 random variables from the geometric distribution.
3. Calculate some basic statistics:

mean_x <- mean(x)

var_x <- var(x)

sd_x <- sd(x)
4. Print the results in item 3 with the following output (string): 

Number of trials required to achieve first success:

Mean (in 2 decimal places):

Variance (in 2 decimal places):

Standard deviation ( in 2 decimal places):

5. Plot the histogram of the results.
```{r probability,  echo=FALSE}
# Set the probability of success
p <- 0.2

# Generate 1000 random variables from the geometric distribution
x <- rgeom(1000, p)

# Calculate some basic statistics
mean_x <- mean(x)
var_x <- var(x)
sd_x <- sd(x)

# Print the results
cat("Number of trials required to achieve first success:\n")
cat("Mean (in 2 decimal places): ", sprintf("%.2f", mean_x), "\n")
cat("Variance (in 2 decimal places): ", sprintf("%.2f", var_x), "\n")
cat("Standard deviation (in 2 decimal places): ", sprintf("%.2f", sd_x), "\n")

# Plot the histogram
hist(x, main="Histogram of Geometric Distribution", xlab="Number of trials", ylab="Frequency", col="lightblue", border="black")

```


## Question (2)
II. Hypergeometric Distribution.  Consider a plant manufacturing IC chips of which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

1.) A sample of 10 is selected from a box of 40;

2.) A sample of 10 is selected from a box of 5000.


```{r hypergeom, echo=FALSE}
# Function to calculate hypergeometric probability
hypergeom_prob <- function(N, K, n, k) {
  choose(K, k) * choose(N - K, n - k) / choose(N, n)
}

# Scenario 1: A sample of 10 is selected from a box of 40
N1 <- 40
K1 <- 0.1 * N1
n1 <- 10

# Calculate the probability of more than 10% defectives
prob1 <- sum(sapply(1:(n1 - 1), function(k) hypergeom_prob(N1, K1, n1, k)))

cat("Probability of more than 10% defectives in Scenario 1:", sprintf("%.4f", prob1), "\n")

# Scenario 2: A sample of 10 is selected from a box of 5000
N2 <- 5000
K2 <- 0.1 * N2
n2 <- 10

# Calculate the probability of more than 10% defectives
prob2 <- sum(sapply(1:(n2 - 1), function(k) hypergeom_prob(N2, K2, n2, k)))

cat("Probability of more than 10% defectives in Scenario 2:", sprintf("%.4f", prob2), "\n")


```
